Ensemble Stability of Biological Networks

### 2014-09-22 paper.tex
remove extra occurrence of Table

Using this approach the probability of \emph{a priori} stability and of robustness for all two component systems is given in Table \ref{tab:structstabmat}. Similarly, the analogous results for all three component systems are computed using Monte Carlo integration and shown in \ref{tab:structstabmat3} and \ref{fig:combined}B.

>>>>

Using this approach the probability of \emph{a priori} stability and of robustness for all two component systems is given in \ref{tab:structstabmat}. Similarly, the analogous results for all three component systems are computed using Monte Carlo integration and shown in \ref{tab:structstabmat3} and \ref{fig:combined}B.
